Describing the C-space of asynchronous periodic task using DIT

### 2013-07-23 dit-paper_ieee.tex

			A region of $\mathbb{N}^n$ can be described by a list of parametric linear constraints describing the convex hull of the admissible points. In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\

			For the synchronous case, the DBF test gives us a list of constraints which, taken together, are a necessary and sufficient condition of feasibility. Those are:
			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). The constraints are thus indeed linear.\\

			However, this description contains an infinite number of constraints, most of which are redundant. While this does not harm the precision of the description, an more efficient description is preferred as it can greatly reduce computation times. The next section gives a method to reduce the size of the description.

			\subsubsection{Removing redundancy}

			In the synchronous case, is has been shown that the constraints corresponding to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are necessary and sufficient to test the feasibility.\\

			Even then, the number of constraints to consider is exponential in the number of tasks. While it has been shown that intervals ending after the end of the busy period are also redundant, this value depends on the $C_i$ and is therefore not usable. The following concept is thus introduced, which is similar to the end of the busy period but which does not depend on the execution times.

@@

			\begin{remark} (from the definition):
				\begin{itemize}
					\item Contrary to the idle times, the DITs are independent of the scheduling or the execution times 			of the jobs.
					\item In feasible system, every DIT is an idle time.
					\item In feasible system, the first DIT happens after the end of the busy period.
					\item As $H$ is always a DIT, we have $t_d \leq H$.
				\end{itemize}
			\end{remark}

			Every DIT being an idle instant, the execution of the system after it does not depend on what happened previously. Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to consider every interval $[0, t]$ with $t$ being a deadline before the first DIT.\\

			To summarize, we reduced the description of the C-space from an infinite number of constraints to only the 			constraints where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job. Note that this is still 			exponential in the number of tasks.

  \subsection{Our work}

  In this paper, we extend the work of \cite{george2009characterization} to the asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the asynchronous case called first periodic DIT ($t_d$), along with an algorithm to find its value. In Section \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is sufficient to consider.

@@

\begin{figure}[h]
$$
\begin{array}{r||c|c|c|l}
    & \text{Incomplete} & \text{Transitive} & \text{Stationary} & \cdots \\
   \text{Name} & \text{period} & \text{period} & \text{period}  & \\
  \hline
  \text{size} & O_{max} & H & H & \cdots \\
  \hline
  t \geqslant & 0 & O_{max} & O_{max} + H & \cdots
\end{array}
$$
\begin{center}
\caption{Behavior of an asynchronous system under EDF.}
\label{fig:asyncBehavior}
\end{center}
\end{figure}

>>>>

			A region of $\mathbb{N}^n$ can be described by a list of parametric linear
			constraints describing the convex hull of that region. In other words, a
			list of conditions which can unequivocally decide if a point is included in the region or not.\\

			For the synchronous case, the DBF test gives us a list of inequations
			on the WCET values of the task set which together are a necessary and
			sufficient condition of feasibility. They can all be written in the
			following way:
			\[
				\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
				t_1 \leq t_2
			\]
			Note that for a given $t$, we have that the $n_i(t)$ are
			constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.\\

			However, this description contains an infinite number of constraints, most of
			which are redundant. While this does not harm the precision of the
			test, the smallest description is preferred as it can greatly
			reduce the computation time of practical feasibility tests using this system
			of inequations. In Section~\ref{sct:removeRedundancy} a method to reduce the size of this set of constraints is given.

	\subsection{Removing redundancy}
		\label{sct:removeRedundancy}

	In the synchronous case, is has been shown that the inequations corresponding
	to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are
	necessary and sufficient to test the feasibility of a system.\\

	Even then, the number of inequations to consider is exponential in the number
	of tasks. While it has been shown that constraints that cover intervals ending
	after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
	therefore not usable, or at least not for the purposes of this paper. The
	following concept is thus introduced, which is similar to the end of the busy period but which does not depend on the execution times.

@@

	\begin{remark} (from the definition):
		\begin{itemize}
			\item Contrary to other idle times, DITs are independent of the
			scheduling or the execution times of the jobs.
			\item In a feasible system, every DIT is an idle time.
			\item In a feasible system, the first DIT happens at the end of the
			first busy period.
			\item As $H$ is always a DIT in synchronous systems, we have at least $t_d
			\leqslant H$ in this case.
		\end{itemize}
	\end{remark}

	Every DIT being an idle instant, the execution of the system after a DIT does
	not depend on what happened before. Because the synchronous arrival pattern is
	the worst case [citation needed], it is sufficient for the DBF test to only
	consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\

	To summarize, we reduced the description of the C-space from an infinite number
	of constraints to only the inequations where $t_1 = 0$, $t_2 \leqslant t_d$ and
	values of $t_2$ correspond to job deadlines. Note that the number of
	constraints is still exponential in the number of tasks.

	\subsection{Our work}
		In this paper, we extend the work of \cite{george2009characterization} to the
		asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
		the concept of DIT adapted to the asynchronous case called first periodic DIT
		($t_d$), along with an algorithm to find its value. In Section
		\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
		system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
		sufficient to consider.

@@

\begin{figure}[h]
	\[
		\begin{array}{r||c|c|c|l}
			& \text{Incomplete} & \text{Transitive} & \text{Stationary} & \cdots \\
			\text{Name} & \text{period} & \text{period} & \text{period}  & \\
			\hline
			\text{size} & O_{max} & H & H & \cdots \\
			\hline
			t \geqslant & 0 & O_{max} & O_{max} + H & \cdots
		\end{array}
	\]
	\begin{center}
	\caption{Behavior of an asynchronous system under EDF.}
	\label{fig:asyncBehavior}
	\end{center}
\end{figure}
